Random Forests", BUAs

### 2024-02-12 src/bua_RF.Rmd
bua

@@

df <- df %>% left_join(lookup.region %>% 
                         filter(WHOLE_PART=="Whole") %>% 
                         dplyr::select(BUA22CD, RGN22CD, RGN22NM), 
                       by = c("BUA22CD" = "BUA22CD")) %>% 
  #filter(is.na(RGN22CD))                                      #142 BUA in more than one regions dropped
  relocate(c(RGN22NM, RGN22CD), .after=BUA22NM) %>% 
  ungroup()

@@

# out.path <- paste0(path, "/data/temp/df_for_bua_rf.csv")
# df <- read_csv(out.path)
# df %>% write_csv(file = out.path)

@@

# detectCores()
cl <- makePSOCKcluster(4)
registerDoParallel(cl)

@@

```{r}
# create a list of the above model outputs
filenames <- list.files(paste0(path, "/outputs/rf/models/oa_rf/regions"), pattern = "*.RData", full.names = T)

for (i in filenames){
  load(file = i)
  i <- gsub("/home/nw19521/projects/web.diffusion/outputs/rf/models/oa_rf/regions/|.RData", "", i)
  assign(i, model.all)  
}

 fit.model.all <- mget(ls(pattern = "^region_"))

# create a list of the above model outputs
fit.model.all <- mget(ls(pattern = "^model.allE|^model.allN|^model.allW|^model.allS"))

@@

df.predictions <- data.frame()
for (i in regions){
  #for (j in regions[!regions == i]){
    pred <- predict(fit.model.all[names(fit.model.all)==paste0("model.all", i)], 
                    df[df$RGN22CD==i,])
    pred <- as.data.frame(pred)
    rownames(pred) <- c()
    assign(paste0("region.predict.model.", ".on.", i), pred)

@@

path.out <- paste0(path, "/outputs/rf/test_regions_BUA.csv")

>>>>

```{r}
# out.path <- paste0(path, "/data/temp/df_for_bua_rf.csv")
# df <- read_csv(out.path)
# df %>% write_csv(file = out.path)

@@

df <- df %>% left_join(lookup.region %>% 
                         #filter(WHOLE_PART=="Whole") %>% 
                         dplyr::select(BUA22CD, RGN22CD, RGN22NM), 
                       by = c("BUA22CD" = "BUA22CD")) %>% 
  #filter(is.na(RGN22CD))                                      #142 BUA in more than one regions dropped
  relocate(c(RGN22NM, RGN22CD), .after=BUA22NM) %>% 
  ungroup()

@@

@@

# detectCores()
cl <- makePSOCKcluster(6)
registerDoParallel(cl)

@@

```{r}
# create a list of the above model outputs
fit.model.all <- mget(ls(pattern = "^model.allE|^model.allN|^model.allW|^model.allS"))

@@

df.predictions <- data.frame()
for (i in regions){
    pred <- predict(fit.model.all[names(fit.model.all)==paste0("model.all", i)], 
                    df[df$RGN22CD==i,])
    pred <- as.data.frame(pred)
    rownames(pred) <- c()
    assign(paste0("region.predict.model.", ".on.", i), pred)

@@

path.out <- paste0(path, "/outputs/rf/figures/test_regions_BUA.csv")
